Practical Considerations for Lomb-Scargle Periodic Analysis

### 2016-11-15 paper.tex
Add Figures 1 and 2

[Quick motivating example with figures: RR Lyrae star from LINEAR?]

\section{Measuring Periods in Continuous Signals}

@@

\begin{equation}
  \hat{g}(\omega) = \int_{-\infty}^\infty g(t) e^{-2\pi i \nu t} dt
\end{equation}

@@

\begin{equation}
  \{g \ast h\}(t) = \int_{-\infty}^\infty g(t - \tau) h(\tau) d\tau
\end{equation}

@@

\subsubsection{$\mathcal{F}$ of a Gaussian is a Gaussian}
One of the special functions under a Fourier transform is the Gaussian distribution, which is proportional to

>>>>

The Lomb-Scargle periodogram is a classic algorithm for detecting periodicity
in unevenly-sampled time-series, particularly within the astronomy community.
For example, consider the data showing in \Fig{LINEAR_data}.
This is an irregularly-sampled timeseries showing a single object from the
LINEAR survey, with magnitude measured 280 times over the course of five and
a half years.

It is clear that this object varies with an amplitude of around 0.6 magnitudes.
Computing the Lomb-Scargle periodogram for the data gives us a measure of the
power as a function of period of oscillation (\fig{LINEAR_power}, left), from
which we can determine the period of oscillation of approximately 2.58 hours.
The right panel of \fig{LINEAR_power} shows a folded visualization of
the same data as \fig{LINEAR_data} -- i.e.{} plotted as a function of phase
rather than time.

Often this is exactly how the Lomb-Scargle periodogram is presented: as a clean
procedure to detect the periodic component in an unevenly-sampled dataset.
In practice, however, there are a number of subtle issues that must be considered
when applying a Lomb-Scargle analysis to real-world datasets.
This paper contains a practical guide to the effective use of the Lomb-Scargle
periodogram for analyzing real-world time-series.

\begin{figure}[ht]
\centering
\includegraphics[width=\textwidth]{fig01_LINEAR_data}
\caption{Observed light curve from LINEAR object ID 11375941
    \figlabel{LINEAR_data}.
}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=\textwidth]{fig02_LINEAR_PSD}
\caption{{\it Left panel:} the Lomb-Scargle periodogram computed from the data
    in \fig{LINEAR_data}, with an inset detailing the interesting region.
    {\it Right panel:} the input data in \fig{LINEAR_data}, folded over the
    2.58-hour period to show the coherent periodic variability.
    \figlabel{LINEAR_power}
}
\end{figure}

\section{Background: Periods in Continuous Signals}

for a continuously defined signal $g(t)$, the Fourier transform is $\hat{g}(\nu)$,

\begin{equation}
    \mathcal{F}\left\{g\right\}(f) = \int_{-\infty}^\infty g(t) e^{-2\pi i f t} dt
\end{equation}

@@

\begin{equation}
  \mathcal{F}\left\{g\right\}(f) = \int_{-\infty}^\infty g(t) e^{-2\pi i f t} dt
\end{equation}

The inverse of this operation is

\begin{equation}
  \mathcal{F}^{-1}\left\{g\right\}(f) = \int_{-\infty}^\infty g(t) e^{+2\pi i f t} dt
\end{equation}

@@

\begin{equation}
  \{g \ast h\}(t) \equiv \int_{-\infty}^\infty g(t - \tau) h(\tau) d\tau
\end{equation}

@@

\subsubsection{$\mathcal{F}$ of a Gaussian is a Gaussian}
One of the special functions under a Fourier transform is the Gaussian distribution:

\begin{equation}
    g(t; \mu, \sigma) = \frac{1}{\sqrt{2\pi\sigma^2}} \exp\left[\frac{- (x - \mu)^2}{2\sigma^2}\right]
\end{equation}, which is proportional to
